Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-24 paper/paper.tex

- unit of observation: city-year / city-period
- precision of time points
- aggregation of years
- unbalanced panel
- definition of territory holding
- definition of switch in period
- justification for using construction
- different groupings of construction
- scope of the data / regions included
- time period recorded
- missing values / full sequence of event years
- dropNA construction -> sample size

@@

\begin{figure}
    \centering
    \includegraphics{}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

>>>>

- unit of observation: city-year / city-period
- precision of time points
- aggregation of years
- unbalanced panel
- definition of territory holding
- definition of switch in period
- justification for using construction
- different groupings of construction
- scope of the data / regions included: 1937 germany
- time period recorded
- missing values / full sequence of event years
- dropNA construction -> sample size

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.15]{paper/output/descriptive/map_cities.png}
    \caption{Distribution of cities in the assembled dataset. Polygons on the map do \textbf{not} represent historical borders; they merely represent regions by which cities are clustered in the \textit{Städtebuch}. The polygons are computed as convex hulls of the city locations in each region because geo-referenced borders of regions were not available --- this results in some overlap.}
    \label{fig:map_cities}
\end{figure}
